A thesis draft

### 2018-11-23 res/sections/15-ArchitecturalImplementation.tex
Add something

Our first step was to try to use Openstack to create a container orchestration. 
The reason behind this approach was simple: Openbaton, on paper, provides an 
out-of-the-box support for Openstack. In fact, it natively supports Openstack 
PoPs, giving to us a great possibility to reuse the two frameworks and to ease 
the development phase of our software.
\subsection{Openstack for developers: Devstack}
% TODO talk about Devstack installation

>>>>

Our first step was to try to use Openstack to create a container orchestration. 
The reason behind this approach was simple: Openbaton, on paper, comes with an 
out-of-the-box support for Openstack. In fact, it natively supports Openstack 
PoPs, giving to us a great possibility to reuse the two frameworks and to ease 
the development phase of our software.
\subsection{Openstack for developers: Devstack}
Openstack is composed by modules, giving the possibility to the user who wants 
to install it to choose only the components it really needs. So the first thing 
we decided was to perform a selection of these modules between the 33 available 
in the installation page.
% TODO talk about Devstack installation
